Polytope notes

### 2020-01-20 notes/polytope-notes.tex
Reworded a couple things, but not too many changes.

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{conjecture}{Conjecture}
\newtheorem{claim}{Claim}

@@

  \section{Starting with polytopes}\label{sec:start-polytope}
  In this section, we will suppose we start with a finite set of $n$ polytopes $\T := \{T_1, \ldots, T_n\}$, and we will call $T := T_1 \oplus \ldots \oplus T_n \in \reals^d$ their Minkowski sum.
  We know that every polytope has both a halfspace and vertex representation ($\H$-representation and $\V$-representation, respectively.)
  In order to construct the $\H$-representation, we know there must be a matrix $V \in \reals^{k \times d}$ and vector $e \in \reals^k$ such that $T = \{x \in \reals^d : Vx \leq e\}$, but it is unclear how to find such a set, which we discuss in Section~\ref{sec:find-V}.

  \subsection{Notation and new definitions}
  We will use the following notation throughout the rest of this section.
  Suppose we are given a polytope $T_y \in \reals^d$ and set of vectors $V \in \reals^{k \times d}$.
  Call $e^y \in \reals^k$ the vector such that $e^y_i = \max_{x \in T_y}\inprod{v_i}{x}$.  
  For a finite set $\T = \{T_1, , \ldots, T_n\}$, let us denote the matrix $E = (e^y)_{y=1}^n$.
  \begin{definition}
    We say a set of normals $V$ is \emph{complete} with respect to a polytope $T_y$ if $T_y = \{x \in \reals^d: Vx \leq e^y\}$.
  \end{definition}
  Moreover, we say $V$ is complete with respect to the set of polytopes $\T$ if and only if $V$ is complete with respect to each $T_y \in \T$.

  \subsection{Finding $V$}\label{sec:find-V}
  \btw{Not sure if we want to go this far, or just argue that a complete set of normals exists.  This would be where Corollaries 1 and 2 come in though.}
  In order to find a matrix of normals $V$ that is complete with respect to $T := \oplus_y T_y$, we can look at the normal cones for each $T_y$ and find a vector in the normal cone $\N(F_y, T_y)$ in the decomposition of $F$ in $T$ for each face $F$.
  Since we know $T_1, \ldots, T_n$ are polytopes and therefore have $\H$-representations, one of the first natural steps is to find a set of valid inequalities describing each $T_y$.
  For each face $F_j$ of the Minkowski sum polytope 
  $T$, we can choose a normal $v_j \in \N(F_j; T)$ and describe the face $F$ by $\{x \in T:  \inprod{v_j}{x} = \sup_{x \in T} \inprod{v_j}{x} =: e_j\}$ by Theorem~\ref{thm:unique-face-decomp} and Definition~\ref{def:face}.
  For each face $F_{j}^{y}$ that is in the decomposition of the face $F_j$, we have $\inprod {v_j}{x} \leq e^y_j$ forming a tight bound on $F_j$ by Theorem~\ref{thm:support-minksum}.

  For ease of notation, we concatenate the $e^y$ vectors corresponding to the support of each normal defining the polytope $T_y$ to form the matrix $E$ according to a consistent ordering on $\Y$.
  Note that as we assume $V$ is complete with respect to $\T$, we have $e^y$ having the same dimensions for all $y$, and thus $E$ is a matrix.

%  Therefore, if we take a matrix $V$ that is a finite set of the elements of the normal cones for each face in $T$, such a matrix can also be used to define the $\H$-representation for not only $T$, but each $T_y$.
%  For each face $F_i$ of $T$ with $\N(F_i, T) \neq \emptyset$, we can choose one normal $v_i$ so that the face $F_i = \{x : \inprod{v_i}{x} = \sup_{x\in T}\inprod{v_i}{x} =: e_i\}$.
%  As this happens for each face with a nonempty normal cone, we can repeat this for each $T_y \in \T$.
%  This yields the matrix $E := (e_{yj})$ where $e_{yj} = \sup_{x \in T_y}\inprod{v_j}{x}$.
%

  \begin{proposition}\label{prop:complete-V}
  	The normals $V$ constructed by taking an element of the normal cone $\N(F, T)$ for each face $F$ in $T$ is complete for both $T$ and each $T_y \in \T$.
  \end{proposition}
  \begin{proof}
  	First, to see this constructed $V$ is complete for $T$, consider that the normals to the facets (in the affine span of $T$) of $T$ is complete for $T$.
  	Moreover, each additional normal is a redundant constraint, so
%   since the inner product of elements of the normal cone is less than or equal to the support for the polytope for every element of $T$.
%  	Thus, 
  	$V$ is complete for $T$.

  	To see why $V$ is complete with respect to each $T_y$, consider each case of subset inclusion.
  	We will let $\bar T_y := \{ x : Vx \leq e^y\}$ be the polytope described by $V$ and $E$, and $T_y$ be the given polytope.

  	First,  to see $T_y \subseteq \bar T_y$, take $x \in T_y$.
  	For all $i \in [k]$, we then have $\inprod{v_i}{x} \leq H_{T_y}(v_i) = e^y_i$.
  	By definition, this holds for all $v_i$ such that $v_i \in \N(F, T_y)$ for some $F$ a face of $T_y$.
  	We then want to claim that, for all $v_i \in V$, there is some face $F_y$ of $T_y$ such that $v_i \in \N(F_y, T_y)$, and thus the previous statement holds.
  	This follows from Corollary~\ref{cor:face-decomp-normal-cones}, since we know that we must have $v_i \in \N(F, T)$ for some face $F$ of $T$ by construction.
  	We necessarily have $v_i \in \N(F_y, T_y)$, where $F_y$ is the face of $T_y$ in the decomposition of $F$.

  	Now to see $\bar T_y \subseteq T_y$, we use a contradiction.
  	Suppose there was some $x \in \bar T_y$ such that $x \not \in T_y$.
  	Then there must be some $v_i \in V$ so that $\inprod {v_i}{x} > \sup_{y \in T_y} \inprod{v_i}{y}$.
  	This implies that for all faces $F_{j}^y$ of $T_y$, we have $v_i \not \in \N(F_{j}^y, T_y)$.
  	However, by construction of $V$, we can consider the face $F$ of $T$ such that $v_i \in \N(F,T) = \cap_y \N(F_y, T_y)$ by Corollary~\ref{cor:face-decomp-normal-cones}.
  	We necessarily have $v_i \in \N(F_y, T_y)$, yielding a contradiction.
  	Thus, we have $v_k \in \N(F_y, T_y)$, so we conclude $\bar T_y \subseteq T_y$, yielding the equality of each $\bar T_y = T_y$, which is the statement.
  \end{proof}

  The construction of $V$ in Proposition~\ref{prop:complete-V} is typically not the minimal $V$ that is complete for $\T$.
  By minimal, we mean that the number of normals $k$ is minimized while still being complete.
  It is unclear at the current moment how to find such a minimal set of normals, so we proceed to understanding what we can say once we have $V$.

  \subsection{Once we have $V$}
  Now, for a given polytope $T(p)$, we will later want to ask when a given $z \in \reals^d$ is in the polytope $T(p)$.
  We will then use this to understand the set of $p \in \simplex$ for which $z \in T(p)$, later substituting $z=0$.
  Throughout, assume we have $V$ which is complete for $\T$ and $E$ defined by the support of each normal in $V$ for all $T_y \in \T$.
  As a reminder, we denote $e^y = E_{;y}$ as the $y^th$ column of $E$, or equivalently, the support vector for $T_y$ given $V$.

  Since we define $T_y = \{x : Vx \leq e^y\}$, we can multiply the right side of the inequality by the constant $p_y \geq  0$ to yield $p_y T_y = \{x : Vx \leq p_y e^y\}$.
  Now in taking the Minkowski sum of polytopes described by the same set of normals, we can take 
  \begin{align*}
  \oplus_y p_y T_y &= \{x : Vx \leq p_1 E_{;1}\} \oplus \ldots \oplus \{x : Vx \leq p_n E_{;n}\} \\
  &= \{x : Vx \leq p_1 E_{;1} + \ldots + p_n E_{;n}\}\\
  &= \{x : Vx \leq E p\}~.~
  \end{align*}
  The first to second line follows from Theorem~\ref{thm:support-minksum} and preservation of inequalities under addition.
  Now, we have $z \in T(p) \iff \inprod{v_i}{z} \leq (Ep)_i$ for all $v_i \in V$.

  We are particularly interested in when $\vec 0 \in T(p)$, we have $\vec 0 \in T(p)$ if and only if $E p \geq 0$ by substitution.  \btw{For later, common result to say $T(p) = \partial \inprod p {L(\cdot)}$, so if $0 \in T(p)$, we have a minimizer of the loss.}

@@

  \section{Starting at the cell $C$}\label{sec:start-cell}

  Now let us consider some cell $C \subseteq \simplex$.
  Let $A$ be the affine span of the simplex, $A := \{p \in \reals^n : \sum_y p_y = 1\}$.
  We can represent the cell $C := \{p \in A : Bp \geq c\}$.
  In fact, we can set $c := \vec 0$ in order to enforce a unique representation of $B$, up to row reordering and scaling.
  This also allows us to use the same matrix for the $\H$-representation even as we scale the simplex by a positive constant.

  Here, unlike the matrix $E$ when given $V$, the matrix $B$ is not unique.
  In a similar manner, we can simply add redundant constraints in $A$ and yield the same cell $C$.

  \subsection{Notes post NeurIPS} 
  Still not sure if we can construct $B$ with the assumption that $p \in \simplex$ rather than $p \in A$, but gathering from our conversations at NeurIPS, that question seems worth investigating, just maybe after COLT.
  I mean that in the sense that this $B$ matrix captures our necessary condition.
  The vertex representation seems to capture our sufficient condition, possibly rendering the simplex halfspace constraints unnecessary when we think of them as necessary conditions.
  With the results below (that nonsimplex constraints must appear in both $E$ and $B$), being able to assume the simplex for $B$ would simplify a bit... but doesn't give us a polytope construction by any means.

  \section{Equivalences; moving from polytopes to cells and back}

  In the big picture, we want to know two things.
  First, if we are given a cell $C$, how we can come up with a finite set of polytopes $\T = \{T_1, \ldots, T_n\}$ such that $\vec 0 \in T(p) \iff p \in C$.
  Second, we want to know the opposite case: starting from $\T$, can we derive the cell $C \subseteq \simplex$ where $\vec 0 \in T(p)$ for all $p \in C$?

@@

  \begin{lemma}\label{lem:describe-D}
    Suppose we have polytopes $\T = \{T_1, \ldots, T_n\}$ and a set of normals $V$ that is complete for $\T$.
 	Take $E = (e_{i}^y)$ where $e_{i}^y = \max_{x \in T_y} \inprod{v_i}{x}$, and $D = \{p \in \simplex : Ep \geq \vec 0\}$.

@@

    Each halfspace is bounded by the support function of the weighted polytope by construction of $E$, so the support of the weighted polytope defined by an inequality on $v_i$ can be described as $\inprod{v_i}{z} \leq \inprod{E_i}{p}$.
    Taking this for all $v_i$, we then have $T(p) = \oplus_y p_y T_y = \{x \in \reals^d : Vx \leq Ep\}$.

    Therefore, for fixed $p$, we have $\vec 0 \in \oplus_y p_y T_y \iff Ep \geq \vec 0$.
    Since this is true for all $p \in \simplex$, we observe the stated set equality.
  \end{proof}

  \begin{proposition}\label{prop:relate-E-B}
    Suppose we have polytopes $\T = \{T_1, \ldots, T_n\}$ and a set of normals $V$ that is complete for $\T$.
    Take $E = (e_{iy})$ where $e_{iy} = \max_{x \in T_y} \inprod{v_i}{x}$, and take $D = \{p \in \simplex : Ep \geq \vec 0\}$ and $C = \{p \in A : Bp \geq \vec 0\}$.

    Then $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = C$	if and only if $C = D$.
    \btw{whiteboard: ``stuff about $E$ and $B$.''}
  \end{proposition}
  \begin{proof}
  	By Lemma~\ref{lem:describe-D}, we have $D = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$ by construction, so the result follows from substitution.
  \end{proof}

  \begin{definition}
  	We say a vector $v$ is \emph{redundant} with respect to matrix $Y$ if we have $\{z \in A : Yz \geq \vec 0\} = \{z \in A : [Y;v]z \geq \vec 0\}$.
  \end{definition}

  \begin{proposition}\label{prop:relate-rows}
  	Suppose we have polytopes $\T = \{T_1, \ldots, T_n\}$ and a set of normals $V$ that is complete for $\T$.
  	Take $E = (e_{i}^y)$ where $e_{i}^y = \max_{x \in T_y} \inprod{v_i}{x}$, and take $D = \{p \in \simplex : Ep \geq \vec 0\}$ and $C = \{p \in A : Bp \geq \vec 0\}$.

  	Then $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = C$	if and only if non-simplex rows of $B$ appear in $E$ (possibly scaled) and every other row of $E$ is redundant with respect to $B$.
  	\btw{``replace prop 1 statement with `non-simplex rows of $B$ appear in $E$ (possible scaled) and every other row of $E$ is redundant with respect to $B$.'''}
  \end{proposition}
  \begin{proof}
	\begin{itemize}
		\item [$\implies$] First, assume $C = \{p \in \simplex: \vec 0 \in \oplus_y p_y T_y\}$.
		By Proposition~\ref{prop:relate-E-B}, we know that $C = D := \{p \in \simplex : Ep \geq \vec 0\}$.
		We can re-write $D$ as $\{p \in A : [E;I_n] p \geq \vec 0\}$, building simplex constraints into the inequality rather than the domain assumption.
		By the assumed equality, every row of $B$ must then appear in $[E;I_n]$, where $I_n$ is the $n$-element identity matrix.
		As $\{p \in A : I_n p \geq \vec 0\}$ strictly defines the simplex, any non-simplex row of $B$ must then be described by a row of $E$, up to rescaling.

		What's more is that since the polytopes are the same, they have a unique minimal $\H$-representation (up to rescaling) since they are defined by an inequality on $\vec 0$.
		\btw{Elaborated this justification in the comment below ``As $D$ is defined... yielding a contradiction.''}
%		As $D$ is defined by distributions on $\simplex$ and $C$ on $A$, and $\simplex \subset A$, we have the rest of the rows in $E$ necessarily being redundant with respect to $B$.
%		To see this, suppose there was a row of $E$ that was not redundant with respect to $B$.
%		If such a row did not partition the simplex, it would necessarily be redundant by the restriction that $C \subseteq \simplex$.
%		Thus, such a row much partition the simplex, but not appear in $B$ up to rescaling.
%		Again, if the constraint does not partition the cell, the constraint is redundant, and if it does, then $C \neq D$, yielding a contradiction.

		\item [$\impliedby$] Suppose that any non-simplex rows of $B$ appear in $E$, and every other row of $E$ is redundant with respect to $B$.
		Then we have $D = \{p\in \simplex : Ep \geq \vec 0\} = \{p \in \simplex : Bp \geq \vec 0\}$.
		This polytope is equal to $\{p \in A : Bp \geq \vec 0\} = C$ since we require $C\subseteq \simplex$, so $B$ encapsulates any non-redundant simplex constraints.

		Then $D = C$, and therefore, by Proposition~\ref{prop:relate-E-B}, we have $C = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$.
	\end{itemize}
  \end{proof}

%  \bigskip
%  \hrule
%  \bigskip
%
%  \section{Necessary and sufficient conditions}
%  \btw{This probably shouldn't be in this document... let's move it later.}
%  \subsection{Necessary conditions}
%    Halfspace representation
%  \subsection{Sufficient conditions}
%    Vertex representation

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

>>>>

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{conjecture}{Conjecture}
\newtheorem{condition}{Condition}
\newtheorem{claim}{Claim}

@@

  \subsection{Notation and new definitions}
  We will use the following notation throughout the rest of this section.
  Suppose we are given a polytope $T_y \in \reals^d$ and set of vectors $V \in \reals^{k \times d}$.
  Call $e^y \in \reals^k$ the vector such that $e^y_i = \max_{x \in T_y}\inprod{v_i}{x}$.  
  For a finite set $\T = \{T_1, , \ldots, T_n\}$, let us denote the \emph{support matrix} $E = (e^y)_{y=1}^n$.
  \begin{definition}
    We say a set of normals $V$ is \emph{complete} with respect to a polytope $T_y$ if $T_y = \{x \in \reals^d: Vx \leq e^y\}$.
  \end{definition}
  Moreover, we say $V$ is complete with respect to the set of polytopes $\T$ if and only if $V$ is complete with respect to each $T_y \in \T$.

  \subsubsection*{Optimality Condition}
  In general, we know that $\vec 0$ in the subgradient of $f(r)$ if and only if $r$ is an optimum of convex $f$ in general dimensions.

  For nice\footnote{for reports on the relative interior of the domain, and something else} conditions, we have $\vec 0 \in \oplus_i f_i$ if and only if $\vec 0 \in \oplus_i \partial f_i(r)$.
  This allows us to consider the following optimality condition:
  \begin{definition}\label{def:optimality}[Optimality]
  	For all $r \in \R$ and $y \in \Y$, we have $r \in \gamma_r \iff \vec 0 \in \oplus_y p_y T_y(r)$.
  \end{definition}
  The polytope $T_y(r)$ can be thought of as $\partial L_y(\varphi(r))$.

  \section{From polytopes to cells}\label{sec:start-polytope}
  In this section, we will suppose we start with a finite set of $n$ polytopes $\T := \{T_1, \ldots, T_n\}$, and we will call $T := T_1 \oplus \ldots \oplus T_n \in \reals^d$ their Minkowski sum.
  We know that every polytope has both a halfspace and vertex representation ($\H$-representation and $\V$-representation, respectively.)
  By existence of the $\H$-representation, we know there must be a matrix $V \in \reals^{k \times d}$ and vector $e \in \reals^k$ such that $T = \{x \in \reals^d : Vx \leq e\}$.
  In fact, with a complete set of normals $V$, we know that $e$ can be the support vector of each of the normals.
  However, finding $V$ is not always easy, so we assume that we are given $V$ for now.

  \subsection{Given normals $V$}
  Now, for a given polytope $T(p)$, we want to ask when a given $z \in \reals^d$ is in the polytope $T(p)$.
  We will later generalize to finding the set of $p \in \simplex$ for which $\vec 0 \in T(p)$ by substituting $z= \vec 0$.
  Throughout, assume we have $V$ which is complete for $\T$ and $E$ defined by the support of each normal in $V$ for all $T_y \in \T$.
  We denote $e^y = E_{;y}$ as the $y^{th}$ column of $E$, or equivalently, the support vector for $T_y$ given $V$.

  Since we define $T_y = \{x : Vx \leq e^y\}$, we can multiply the right side of the inequality by the constant $p_y \geq  0$ to yield $p_y T_y = \{x : Vx \leq p_y e^y\}$.
  Taking the Minkowski sum of polytopes described by the same set of normals, we can take 
  \begin{align*}
  \oplus_y p_y T_y &= \{x : Vx \leq p_1 E_{;1}\} \oplus \ldots \oplus \{x : Vx \leq p_n E_{;n}\} \\
  &= \{x : Vx \leq p_1 E_{;1} + \ldots + p_n E_{;n}\}\\
  &= \{x : Vx \leq E p\}~.~
  \end{align*}
  The first to second line follows from Theorem~\ref{thm:support-minksum} and preservation of inequalities under addition.
  Now, we have $z \in T(p) \iff \inprod{v_i}{z} \leq (Ep)_i$ for all $v_i \in V$.

  Observe that we have $\vec 0 \in T(p)$ if and only if $E p \geq 0$ by substitution, which lines up with our optimality condition in Definition~\ref{def:optimality}.

@@

  \subsection{Equivalences}
  In the big picture, we want to know two things.
  First, if we are given a cell $C$, how we can construct a finite set of polytopes $\T = \{T_1, \ldots, T_n\}$ such that $\vec 0 \in T(p) \iff p \in C$.
  Second, we want to know the opposite case: starting from $\T$, can we derive the cell $C \subseteq \simplex$ where $\vec 0 \in T(p)$ for all $p \in C$?
  We start with the latter, leaving the former for future work.

@@

  \begin{lemma}\label{lem:describe-D}
    Suppose we are given polytopes $\T = \{T_1, \ldots, T_n\}$ and a set of normals $V$ that is complete for $\T$.
 	Take $E = (e_{i}^y)$ where $e_{i}^y = \max_{x \in T_y} \inprod{v_i}{x}$, and $D^\T = \{p \in \simplex : Ep \geq \vec 0\}$.

@@

    Each halfspace is bounded by the support function of the weighted polytope by construction of $E$, so the support of the weighted polytope defined by an inequality on $v_i$ can be described as $\inprod{v_i}{z} \leq \inprod{E_i}{p}$.
    Taking this for all $v_i$, we then have $\oplus_y p_y T_y = \{x \in \reals^d : Vx \leq Ep\}$.

    Therefore, for fixed $p$, we have $\vec 0 \in \oplus_y p_y T_y \iff Ep \geq \vec 0$.
    As $p \in \simplex$ was arbitrary, we observe the stated set equality.
  \end{proof}

  \begin{proposition}\label{prop:relate-E-B}
    Suppose we are given polytopes $\T = \{T_1, \ldots, T_n\}$ and a set of normals $V$ that is complete for $\T$.
    Take $E = (e_{iy})$ where $e_{iy} = \max_{x \in T_y} \inprod{v_i}{x}$, and take $D = \{p \in \simplex : Ep \geq \vec 0\}$ and take the minimal rank $B \in \reals^{k \times n}$ such that we have the given cell $C = \{p \in \simplex : Bp \geq \vec 0\}$.

    Then $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = C$	if and only if $C = D$.
    \btw{whiteboard: ``stuff about $E$ and $B$.''}
  \end{proposition}
  \begin{proof}
  	By Lemma~\ref{lem:describe-D}, we have $D = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$, and the result follows.
  \end{proof}

  \begin{definition}
  	We say a vector $v$ is \emph{redundant} with respect to matrix $Y$ if we have $\{z: Yz \geq \vec b\} = \{z : [Y;v]z \geq \vec b^*\}$, where $b^* = [b;c]$ for some constant $c \in \reals$.
  \end{definition}

  \begin{proposition}\label{prop:relate-rows}
  	Suppose we have polytopes $\T = \{T_1, \ldots, T_n\}$ and a set of normals $V$ that is complete for $\T$.
  	Take $E = (e_{i}^y)$ where $e_{i}^y = \max_{x \in T_y} \inprod{v_i}{x}$, and take $D = \{p \in \simplex : Ep \geq \vec 0\}$ and take the minimal matrix $B$ such that a given cell $C = \{p \in \simplex : Bp \geq \vec 0\}$.

  	Then $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = C$	if and only the rows of $B$ appear in $E$ (possibly scaled) and every other row of $E$ is redundant with respect to $B$.
  	\btw{``replace prop 1 statement with `non-simplex rows of $B$ appear in $E$ (possible scaled) and every other row of $E$ is redundant with respect to $B$.'''}
  \end{proposition}
  \begin{proof}
	\begin{itemize}
		\item [$\implies$] First, assume $C = \{p \in \simplex: \vec 0 \in \oplus_y p_y T_y\}$.
		By Proposition~\ref{prop:relate-E-B}, we know that $C = D^\T := \{p \in \simplex : Ep \geq \vec 0\}$.
		Then we have $\{p \in \simplex : Bp \geq \vec 0\} = \{p \in \simplex : Ep \geq \vec 0\}$.
		As $B$ is minimal, we must have that every row of $B$ appears (possibly scaled) in $E$.
		Otherwise, we would contradict equality of the polytopes $C$ and $D$.
		Moreover, all rows in $E$ not in $B$ are redundant with respect to $B$ by equality of the polytopes.

		\item [$\impliedby$] Suppose that all rows of $B$ appear in $E$, and every other row of $E$ is redundant with respect to $B$.
		Then we have $D = \{p\in \simplex : Ep \geq \vec 0\} = \{p \in \simplex : Bp \geq \vec 0\} = C$.

		Then $D = C$, and by Proposition~\ref{prop:relate-E-B}, we have $C = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$.
	\end{itemize}
  \end{proof}

  \section{Necessary and sufficient conditions for optimality}
  \subsection{Necessary conditions}
    With the above results, we actually realize that the matrix $B$ captures a necessary condition for optimality.
    As we showed earlier, we derive the support matrix $E$ such that $\vec 0 \in \oplus_y p_y T_y \iff Ep \geq \vec 0$ by substitution, and in Proposition~\ref{prop:relate-rows}, derive necessary and sufficient conditions on the matrix $B$ such that the optimality condition ($\vec 0$ in the weighted Monkowski sum) holds, and these conditions are in relation to the support matrix $E$.

    \begin{condition}[$\H$-condition]\label{cond:H-condition}
    	Given polytopes $\T$ and the cell $C = \{p \in \simplex : Bp \geq \vec 0\}$, there exist normals $v_1, \ldots, v_k$ such that $\max_{z \in T_y} \inprod{v_i}{z} = B_{iy}$ for all $i \in [k]$ and $y \in [n]$.
    \end{condition}

  \subsection{Sufficient conditions}
    Now in order to think about sufficient conditions for optimality, consider that convex polytopes all have $\V$-representations.
    Therefore, we can equivalently define the cell $C = \{p \in \simplex : Bp \geq \vec 0\} := \conv(\{p^1, \ldots, p^\ell\})$ for a finite set of distributions $p^j \in \simplex$, indexing with $j \in [\ell]$.
    Any distribution $p \in C$ can then be written as a convex combination of $p^j$ making up the convex hull.
%    , so $\vec 0$ being in those Minkowski sums implies that $\vec 0$ is also in the weighted Minkowski sum of any convex combination. \jessiet{Too hand wavy}
    \begin{condition}[$\V$-condition]\label{cond:V-condition}
    	Given $\T$ and $C = \conv(\{p^1, \ldots, p^\ell\})$, there exist $x_{jy} \in T_y$ such that $\oplus_y p^j_y x_{jy} = \vec 0$ for all $j \in [\ell]$.
    \end{condition}

  These two conditions together give us necessary and sufficient conditions for optimality.

  \begin{theorem}
  	Consider $B \in \reals^{k \times n}$ minimally describing $C = \{p \in \simplex : Bp \geq \vec 0\} = \conv(\{p^1, \ldots, p^\ell\})$ for a given convex cell $C$.
  	There exists $\T = \{T_1, \ldots, T_n\}$ such that $D^\T = C$ if and only if there exist normals $v_1, \ldots, v_k$, and points $x_{jy}$ such that the Conditions~\ref{cond:H-condition} and~\ref{cond:V-condition} hold.
  \end{theorem}
  \begin{proof}
  	$\implies$
    First, let there exist polytopes $\T$ so that $D^\T = C$.

    Suppose $V^*$ is complete for $\T$.
    Take $V = [v_1, \ldots, v_k]^T$ to be the normals corresponding to the nonredundant rows of $E$ with respect to $B$.
    Each entry of the support matrix $E$ is equal to $B$ for these nonredundant normals by Proposition~\ref{prop:relate-rows}.
    Therefore, Condition~\ref{cond:H-condition} is satisfied with the constructed set of normals $V$.    
%    Condition~\ref{cond:H-condition} is satisfied by the existence of a halfspace representation of the polytopes $T_y$, which requires a superset $V^*$ of $V = [v_1, \ldots, v_k]^T$ such that $V^*$ is complete for $\T$ and reduction of redundant rows from the support matrix $E$, which make up $B$.

    Moreover, as $\{ p : Ep \geq \vec 0\} \subseteq \{p : Bp \geq \vec 0\}$ (since rows of $E$ are either in $B$ or redundant), we apply Lemma~\ref{lem:describe-D} to observe that there is a witness $x_y \in T_y$ for all $p \in D^\T$ such that $\oplus_y p_y x_y = \vec 0$, as this is a corollary of our optimality condition.
    In particular, this is true for every distribution $p^j \in \{p^1, \ldots, p^\ell\}$, thus Condition~\ref{cond:V-condition} is satisfied.

    \bigskip
    $\impliedby$

    Consider the set of polytopes $\T$ given so that there are normals $v_i$ and witnesses $x_{jy}$ satisfying Conditions~\ref{cond:H-condition} and~\ref{cond:V-condition}.
    With these polytopes, we want to show that $D^\T = C$.

    \bigskip
    $D^\T \subseteq C$.
    \bigskip

    We have $D^\T = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$, and $C = \{p \in \simplex : Bp \geq \vec 0\}$.
    Take $p \not \in C$, and therefore $Bp < \vec 0$, and we will show $p \not \in D^\T$.
    For some row $\bar i$ of $B$, we must have $\inprod{B_{\bar i}}{p} = b < 0$.

    By Condition~\ref{cond:H-condition}, we can write polytopes as $T_y = \{x : \inprod{v_i}{x} \leq B_{iy} \; \forall i \in [k]\}$, since the $max$ being equal $B_{iy}$ implies an inequality on all $x \in T_y$.
    Moreover, by Theorem~\ref{thm:support-minksum}, we know the support of the weighted Minkowski sum is $Bp$, so the Minkowski sum can be written $\oplus_y p_y T_y = \{x : \inprod{v_i}{x} \leq (Bp)_i \; \forall i \in [k] \}$.
    As $(Bp)_{\bar i} < 0$, we have that $\vec 0$ is not in $T(p)$, so we have $p \not \in D^\T$.
    Thus, we have shown the contrapositive and have $D^\T \subseteq C$.

    \bigskip
    $C \subseteq D^\T$.
    \bigskip

    Take $p \in C$ so that $Bp \geq \vec 0$.
    Observe that $D^\T$ is a convex polytope, as there is a complete set of normals $V^*$ for $\T$,\jessiet{haven't shown this in this doc, but doesld be easy enough to argue.} and we know that the support matrix $E$ can be constructed so that $D = \{p \in \simplex : Ep \geq \vec 0\}$, which is convex as it is the intersection of a finite number of halfspaces, bounded by simplex constraints, and closed by the weak inequality.
%    it is bounded by simplex constraints, closed by definition, and convex by \jessie{ARGUE}.
    By Condition~\ref{cond:V-condition}, we have that $p^1, \ldots, p^\ell$ are all in $D^\T$, since such witnesses imply $\vec 0$ is in the weighted Minkowski sum.
    Moreover, as $C = \conv(\{p^1, \ldots, p^\ell\})$, we have $C \subseteq D^\T$.

  \end{proof}
\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
